Covariate analysis of ROSMAP RNASeq

### 2016-10-25 code/Rmd/ROSMAP_RNASeq_Qntl.Rmd
Minor modifications

# Get differnetial expression
DE = list()
p = list()
for (i in 1:3){
  DE[[i]] = topTable(FIT.CONTR, coef=i, number = dim(EXPR)[1])
  DE[[i]] = rownameToFirstColumn(DE[[i]], "ensembl_gene_id") 
  p[[i]] <- ggplot(DE[[i]], aes(x = logFC, y = -log10(adj.P.Val))) + geom_point()
  p[[i]] <- p[[i]] + ggtitle(colnames(contrast)[i])# + xlim(c(-1.5,1.5)) + ylim(c(0,6))
  p[[i]] <- p[[i]] + geom_hline(yintercept = -log10(0.05), color = 'red')
}
multiplot(plotlist=p, cols = 3)
names(DE) = colnames(contrast)

>>>>

# Get differnetial expression
DE = list()
p = list()
for (i in 1:3){
  DE[[i]] = topTable(FIT.CONTR, coef=i, number = dim(EXPR)[1], confint = T)
  DE[[i]] = rownameToFirstColumn(DE[[i]], "ensembl_gene_id") 
  p[[i]] <- ggplot(DE[[i]], aes(x = logFC, y = -log10(adj.P.Val))) + geom_point()
  p[[i]] <- p[[i]] + ggtitle(colnames(contrast)[i])# + xlim(c(-1.5,1.5)) + ylim(c(0,6))
  p[[i]] <- p[[i]] + geom_hline(yintercept = -log10(0.05), color = 'red')
}
multiplot(plotlist=p, cols = 3)
names(DE) = colnames(contrast)
